---
title: "notebook20160629"
author: "Mark Hagemann"
date: "June 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today: working more on learning qsub

- Run a batch file (non-interactive)
- See if it's tolerant to internet interrupts

### Test batch file

```
#!/bin/bash
# declare a name for this job to be sample_job
#PBS -N sample_job
# request a total of 40 processors for this job 
#   (2 nodes and 20 processors(core) per node)
#PBS -l nodes=2:ppn=20
# request 4 hours of wall clock time
#PBS -l walltime=04:00:00
# combine PBS standard output and error files
#PBS -j oe 
# mail is sent to you when the job starts and when it terminates or aborts
#PBS -m bea
# specify your email address 
#PBS -M mark.hagemann@gmail.com.com
 
#change to the directory where you submitted the job 
cd $PROJDIR
mkdir qsubtest
touch qsubtest/test1
sleep 15
touch qsubtest/test2
sleep 15
touch qsubtest/test3
exit 0

```

Good. That worked.


### Combining netCDFs for Kim

```{r}
st1 <- open.nc("data/ncdf/nwm.t00z.short_range.channel_rt.f004.conus.nc_georeferenced.nc")
st2 <- read.nc(st1)
close.nc(st1)

getNC <- function(filename) {
  con1 <- open.nc(filename)
  out <- read.nc(con1)
  close.nc(con1)
  out
}

nclist <- lapply(list.files("data/20151031_runoff/", full.names = TRUE), getNC)

times <- 

RNetCDF::create.nc("data/allRunoff1.ncdf")

```


Here's how it should look:

```{r}
tusc1 <- getNC("data/Tuscaloosa_runoff.nc")

str(tusc1, 1)
```


### Back to GIS computation

Using Bahia Grande as pilot study

Steps:

1. Extract pixels from DEM, shapefile overlay
    - upload shapefile
    

### Plotting large dataset

Finally worked!

- Now do this for full DEM set
- todo$add("make virtual raster for whole DEM set")
    - todo$add("move ROGER dems to structure mirroring external hd")
- todo$add("create overview for this big virtual raster")

First issue when making vrt: "Warning 6: gdalbuildvrt does not support heterogenous projection. Skipping dem/ibwc_2011_1m_2698_62_2.dem" etc.

- Try reprojecting all in parallel
- or use -allow_projection_difference option (though this does not reproject)

todo$add("write batch file for creating overviews")

todo$add("get projection info for usgs, ibwc")

Projection info 

- here's ibwc2006

```
gdalinfo /media/removable/NWCSI_data/DEM/ibwc_2006_1m_2698_40_2_d_2.dem 
Driver: USGSDEM/USGS Optional ASCII DEM (and CDED)
Files: /media/removable/NWCSI_data/DEM/ibwc_2006_1m_2698_40_2_d_2.dem
Size is 393, 484
Coordinate System is:
PROJCS["NAD83 / Texas South",
    GEOGCS["NAD83",
        DATUM["North_American_Datum_1983",
            SPHEROID["GRS 1980",6378137,298.257222101,
                AUTHORITY["EPSG","7019"]],
            TOWGS84[0,0,0,0,0,0,0],
            AUTHORITY["EPSG","6269"]],
        PRIMEM["Greenwich",0,
            AUTHORITY["EPSG","8901"]],
        UNIT["degree",0.0174532925199433,
            AUTHORITY["EPSG","9122"]],
        AUTHORITY["EPSG","4269"]],
    PROJECTION["Lambert_Conformal_Conic_2SP"],
    PARAMETER["standard_parallel_1",27.83333333333333],
    PARAMETER["standard_parallel_2",26.16666666666667],
    PARAMETER["latitude_of_origin",25.66666666666667],
    PARAMETER["central_meridian",-98.5],
    PARAMETER["false_easting",984250],
    PARAMETER["false_northing",16404166.66666667],
    UNIT["Foot",0.3048006096012192],
    AXIS["X",EAST],
    AXIS["Y",NORTH]]
Origin = (1146664.739580000052229,16691800.074819998815656)
Pixel Size = (3.280840000000000,-3.280840000000000)
Metadata:
  AREA_OR_POINT=Point
Corner Coordinates:
Upper Left  ( 1146664.740,16691800.075) ( 98d 0'12.86"W, 26d27'25.53"N)
Lower Left  ( 1146664.740,16690212.148) ( 98d 0'12.93"W, 26d27' 9.80"N)
Upper Right ( 1147954.110,16691800.075) ( 97d59'58.67"W, 26d27'25.48"N)
Lower Right ( 1147954.110,16690212.148) ( 97d59'58.74"W, 26d27' 9.75"N)
Center      ( 1147309.425,16691006.112) ( 98d 0' 5.80"W, 26d27'17.64"N)
Band 1 Block=393x484 Type=Float32, ColorInterp=Undefined
  NoData Value=-32767
  Unit Type: m
```

ibwc2011

```
gdalinfo /media/removable/NWCSI_data/DEM/ibwc_2011_1m_2698_
ibwc_2011_1m_2698_44_2.dem  ibwc_2011_1m_2698_44_4.dem  ibwc_2011_1m_2698_52_2.dem  
ibwc_2011_1m_2698_44_3.dem  ibwc_2011_1m_2698_45_3.dem  ibwc_2011_1m_2698_56_4.dem  
CUAHSI2016:$ gdalinfo /media/removable/NWCSI_data/DEM/ibwc_2011_1m_2698_52_2.dem 
Driver: USGSDEM/USGS Optional ASCII DEM (and CDED)
Files: /media/removable/NWCSI_data/DEM/ibwc_2011_1m_2698_52_2.dem
Size is 7522, 8334
Coordinate System is:
PROJCS["UTM Zone 14, Northern Hemisphere",
    GEOGCS["NAD83",
        DATUM["North_American_Datum_1983",
            SPHEROID["GRS 1980",6378137,298.257222101,
                AUTHORITY["EPSG","7019"]],
            TOWGS84[0,0,0,0,0,0,0],
            AUTHORITY["EPSG","6269"]],
        PRIMEM["Greenwich",0,
            AUTHORITY["EPSG","8901"]],
        UNIT["degree",0.0174532925199433,
            AUTHORITY["EPSG","9108"]],
        AUTHORITY["EPSG","4269"]],
    PROJECTION["Transverse_Mercator"],
    PARAMETER["latitude_of_origin",0],
    PARAMETER["central_meridian",-99],
    PARAMETER["scale_factor",0.9996],
    PARAMETER["false_easting",500000],
    PARAMETER["false_northing",0],
    UNIT["Meter",1]]
Origin = (543064.351441419683397,2904161.798443999607116)
Pixel Size = (0.999947000000000,-0.999976000000000)
Metadata:
  AREA_OR_POINT=Point
Corner Coordinates:
Upper Left  (  543064.351, 2904161.798) ( 98d34' 7.51"W, 26d15'23.40"N)
Lower Left  (  543064.351, 2895827.998) ( 98d34' 8.51"W, 26d10'52.51"N)
Upper Right (  550585.953, 2904161.798) ( 98d29'36.36"W, 26d15'22.51"N)
Lower Right (  550585.953, 2895827.998) ( 98d29'37.53"W, 26d10'51.62"N)
Center      (  546825.152, 2899994.898) ( 98d31'52.48"W, 26d13' 7.53"N)
Band 1 Block=7522x8334 Type=Float32, ColorInterp=Undefined
  NoData Value=-32767
  Unit Type: m
```

usgs 2008

```
gdalinfo /media/removable/NWCSI_data/DEM/usgs_2008_1m_2697_
usgs_2008_1m_2697_17_1.dem  usgs_2008_1m_2697_17_3.dem  usgs_2008_1m_2697_25_1.dem  
CUAHSI2016:$ gdalinfo /media/removable/NWCSI_data/DEM/usgs_2008_1m_2697_25_1.dem 
Driver: USGSDEM/USGS Optional ASCII DEM (and CDED)
Files: /media/removable/NWCSI_data/DEM/usgs_2008_1m_2697_25_1.dem
Size is 6907, 7671
Coordinate System is:
PROJCS["UTM Zone 14, Northern Hemisphere",
    GEOGCS["NAD83",
        DATUM["North_American_Datum_1983",
            SPHEROID["GRS 1980",6378137,298.257222101,
                AUTHORITY["EPSG","7019"]],
            TOWGS84[0,0,0,0,0,0,0],
            AUTHORITY["EPSG","6269"]],
        PRIMEM["Greenwich",0,
            AUTHORITY["EPSG","8901"]],
        UNIT["degree",0.0174532925199433,
            AUTHORITY["EPSG","9108"]],
        AUTHORITY["EPSG","4269"]],
    PROJECTION["Transverse_Mercator"],
    PARAMETER["latitude_of_origin",0],
    PARAMETER["central_meridian",-99],
    PARAMETER["scale_factor",0.9996],
    PARAMETER["false_easting",500000],
    PARAMETER["false_northing",0],
    UNIT["Meter",1]]
Origin = (599231.260636072838679,2945690.377444499637932)
Pixel Size = (0.999986000000000,-1.000039000000000)
Metadata:
  AREA_OR_POINT=Point
Corner Coordinates:
Upper Left  (  599231.261, 2945690.377) ( 98d 0'11.24"W, 26d37'43.06"N)
Lower Left  (  599231.261, 2938019.078) ( 98d 0'13.40"W, 26d33'33.74"N)
Upper Right (  606138.164, 2945690.377) ( 97d56' 1.48"W, 26d37'41.25"N)
Lower Right (  606138.164, 2938019.078) ( 97d56' 3.79"W, 26d33'31.94"N)
Center      (  602684.712, 2941854.728) ( 97d58' 7.48"W, 26d35'37.51"N)
Band 1 Block=6907x7671 Type=Float32, ColorInterp=Undefined
  NoData Value=-32767
  Unit Type: m
```

usgs2011

```
 gdalinfo /media/removable/NWCSI_data/DEM/usgs_2011_2m_2698_29_4.dem 
Driver: USGSDEM/USGS Optional ASCII DEM (and CDED)
Files: /media/removable/NWCSI_data/DEM/usgs_2011_2m_2698_29_4.dem
Size is 3755, 4172
Coordinate System is:
PROJCS["UTM Zone 14, Northern Hemisphere",
    GEOGCS["NAD83",
        DATUM["North_American_Datum_1983",
            SPHEROID["GRS 1980",6378137,298.257222101,
                AUTHORITY["EPSG","7019"]],
            TOWGS84[0,0,0,0,0,0,0],
            AUTHORITY["EPSG","6269"]],
        PRIMEM["Greenwich",0,
            AUTHORITY["EPSG","8901"]],
        UNIT["degree",0.0174532925199433,
            AUTHORITY["EPSG","9108"]],
        AUTHORITY["EPSG","4269"]],
    PROJECTION["Transverse_Mercator"],
    PARAMETER["latitude_of_origin",0],
    PARAMETER["central_meridian",-99],
    PARAMETER["scale_factor",0.9996],
    PARAMETER["false_easting",500000],
    PARAMETER["false_northing",0],
    UNIT["Meter",1]]
Origin = (555397.635084721958265,2938828.056975999847054)
Pixel Size = (1.999893000000000,-2.000096000000000)
Metadata:
  AREA_OR_POINT=Point
Corner Coordinates:
Upper Left  (  555397.635, 2938828.057) ( 98d26'37.51"W, 26d34' 8.67"N)
Lower Left  (  555397.635, 2930483.656) ( 98d26'38.81"W, 26d29'37.45"N)
Upper Right (  562907.233, 2938828.057) ( 98d22' 6.06"W, 26d34' 7.54"N)
Lower Right (  562907.233, 2930483.656) ( 98d22' 7.55"W, 26d29'36.32"N)
Center      (  559152.434, 2934655.857) ( 98d24'22.48"W, 26d31'52.51"N)
Band 1 Block=3755x4172 Type=Float32, ColorInterp=Undefined
  NoData Value=-32767
  Unit Type: m
```

IBWC2006 is lambert conic?! (that's moronic)

todo$add("reproject everything to same CRS")

I'm finally really using `sed`! Have to modify xml for vrt files since I've restructured the folders. 

- `sed 's_relativeToVRT="0"_relativeToVRT="1"_g' <ibwc06vrt.vrt >ibwc06new.vrt`
- `sed 's_/home/cgtrn05/arroyo/dem/ibwc/_DEM/_g' <ibwc06new.vrt >ibwc06vrt.vrt`

Looks like reprojection will be faster to do in parallel and then recombine to vrt. 

todo$add("get index for remaining dems")


Submitting the following file to Roger:

```
#!/bin/bash
# declare a name for this job to be sample_job
#PBS -N 
# request a total of 20 processors for this job 
#   (1 nodes and 20 processors(core) per node)
#PBS -l nodes=1:ppn=20
# request 7 hours of wall clock time
#PBS -l walltime=07:00:00
# combine PBS standard output and error files
#PBS -j oe 
# mail is sent to you when the job starts and when it terminates or aborts
#PBS -m bea
# specify your email address 
#PBS -M mark.hagemann@gmail.com
 
#change to the directory where you submitted the job 
cd /projects/nfie/arroyo/

# Make vrt files
gdalbuildvrt usgsvrt.vrt DEM/usgs*.dem\
gdalbuildvrt ibwc06vrt.vrt DEM/ibwc_2006*.dem\
gdalbuildvrt ibwc11vrt.vrt DEM/ibwc_2011*.dem\


# Reproject all vrt files
gdalwarp -t_srs '+proj=utm +zone=14 +datum=NAD83' ibwc06vrt.vrt ibwc06utm.vrt
gdalwarp -t_srs '+proj=utm +zone=14 +datum=NAD83' ibwc11vrt.vrt ibwc11utm.vrt
gdalwarp -t_srs '+proj=utm +zone=14 +datum=NAD83' usgsvrt.vrt usgsutm.vrt

# Combine to a single vrt
gdalbuildvrt allutm.vrt ./*utm.vrt

# build overview for this vrt
gdaladdo -r average --config COMPRESS_OVERVIEW DEFLATE allutm.vrt 2 4 8 16 32 64 128

exit 0

```