---
title: "notebook20160623"
author: "Mark Hagemann"
date: "June 23, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today I was told to stop working on national-scale stuff and work instead on Arroyo Colorado case study. 

Need to start a new todo list. todo <- TodoList()


Task 1 is understanding lidar data. It resides on an external hard drive, which I have soft-linked to data/softlink

```{r}
ls("package:rLiDAR")
?rMetrics
?LASmetrics

fil1 <- system.file("extdata", "LASexample1.las", package = "rLiDAR")
metrics1 <- LASmetrics(fil1)

metrics1
glimpse(metrics1)
```

There's one rather small file (only 99MB) in the LAS folder. Experiment using this.

```{r}
metrics2 <- LASmetrics("data/ext_softlink/LAS/ibwc_2006_70cm_2697_54_4_b_3.las", 
                       minht = 0.1)
glimpse(metrics2)
```

OK, this package is probably not what I want. It's all about vegetation height and things. 

Unless I can operate manually on the lasfile. 

```{r}
las1 <- rLiDAR::readLAS("data/ext_softlink/LAS/ibwc_2006_70cm_2697_54_4_b_3.las")
```

It's a large matrix--looks like the LAS format comresses it some; here it's about 150% the size on disk. What if I write it to an R binary format?

```{r}
save("las1", file = "data/las1_bin.RData")
```

Yeah, that compressed it a lot! Now it's only 2.4 MB on disk.

```{r}
summary(las1)

las1 %>% 
  as.data.frame() %>% 
  group_by(ReturnNumber) %>% 
  summary()
  glimpse
```

Try plotting

```{r}
library(rgl)

dat1 <- las1 %>% 
  as.data.frame() %>% 
  filter(ReturnNumber == 1) %>% 
  mutate(x = scale(X)[, 1], y = scale(Y)[, 1], z = scale(Z)[, 1])

summary(dat1)

with(sample_n(dat1, 1000), surface3d(x, y, z))
```

Try some more. Contour plots?

```{r}
#with(dat1, contour(interp(X, Y, Z, duplicate = "median")))
```

That took a couple of minutes to run.

Can I plot a convex hull?

```{r}
chull1 <- chull(dat1$X, dat1$Y)

plot(Y ~ X, dat1[chull1, ], type = "l")
```

OK, that's good. What can I learn about lidar data from the readLAS function?

```{r}
readLAS
```

Well the matrix isn't all that's stored in the file. See what else:

```{r}
las2 <- rLiDAR::readLAS("data/ext_softlink/LAS/ibwc_2006_70cm_2697_54_4_b_3.las",
                        short = FALSE)
str(las2, 1)
head(las2)
```

OK, not much new information here. It's still a large matrix, but with the following additional columns: "NumberOfReturns"   "ScanDirectionFlag" "EdgeofFlightLine"  "Classification"  "ScanAngleRank"     "UserData"          "PointSourceID"     "gpstime" 
Although classification might be useful.

```{r}
save("las2", file = "data/las2_bin.RData")
```

Now I'll try a larger file. The next smallest is 10x the size of the last one. 

```{r}
las3 <- readLAS("data/ext_softlink/LAS/ibwc_2006_70cm_2697_46_1_b_2.las")
pryr::object_size(las3)
dim(las3)
save("las3", file = "data/las3_bin.RData")
```

148 MB when in memory, but compresses to 19 MB on disk. 

todo$add("georeference LAS data")
todo$add("plot convex hull for each file")

```{r}


lasChull <- function(file)
```

